Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-29 content/contribution/R4.tex
added that terminal nodes implement instance entailment

 		Finally, terminal nodes receive tokens from the last node in the network and are responsible of producing the new entailed triples.

>>>>

 		Finally, terminal nodes receive tokens from the last node in the network and are responsible of producing the new entailed triples, directly implementing the instance entailment operator $\text{:-}_{head}$ of CoDeR.
